---
title: "eds212-08095A"
author: "Kimmy Wong"
format: html
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---
```{r}
#| message: false
## load tidyverse ----
library(tidyverse)
```

try using 'head()', 'tail()', 'dim()', but don't include it

```{r}
#| include: false
# do some data exploration 
head(starwars)

tail(starwars)

dim(starwars)
```

- create ggplot (scatterplot) of character 'mass' (y-axis) and 'height' (x-axis)
- update the color of the points so its based on 'mass'
- echo on false does not print code on render

```{r}
#| echo: false
ggplot(starwars, aes(x = height, y = mass, colour = mass)) +
  geom_point() +
  labs(x = 'Height (cm)', 
  y = 'Mass (kg)',
  title = 'Title')
```

- create a histogram of character heights
- update fill color to purple and the outside border line of each bin to orange 
- update axis labels
- update code chunk options  so that only code and output graph appear

```{r}
#| fig-cap: "This is my figure caption"
#| fig-alt: "This is some alt text"
ggplot(data = starwars, aes(x = height))+
         geom_histogram(color = "orange", fill = "purple")+
         labs(x = "Character heights (cm)", y = "Count")
```

'df$col_name'

```{r}
sw_height_mean <- round(mean(starwars$height, na.rm = TRUE), digits = 3)
```

The mean height of all starwars characters is `r sw_height_mean`



